---
header-includes:
    - \usepackage{setspace}\doublespacing
output:
  pdf_document: default
  html_document: default
---

\setlength{\abovedisplayskip}{25pt}
\setlength{\belowdisplayskip}{25pt}
\setlength{\abovedisplayshortskip}{25pt}
\setlength{\belowdisplayshortskip}{25pt}

```{r, echo = F}
library(knitr)
if(is_latex_output()) {
  plot_default <- knit_hooks$get("plot")
  knit_hooks$set(plot = function(x, options) { 
    x <- c(plot_default(x, options), "\\vspace{25pt}")
  })
}
```

# Model 1 

```brm(visits ~ autonomous_selfing_level + (1|net_id) + (1|gr(phylo, cov = A))```


This model contains both quantitative and qualitative data of selfing levels and the fixed effect is grouped in 4 categories: "high", "medium", "low" and none levels of selfing. The response variable is the integer of visits. Note that the quantitative measurement that we use is autonomous fruit production. 

Check now the fit of the model:

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=3.5, fig.height=2, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/RData/brms_m1_visits_self_all.RData")
load("Data/RData/brms_data_m1_visits_self_all.RData")

#Model fit
pp_check(m1) + xlim(-100,2000)+ylim(0,0.02)


```

The fit seems right, check now estimates, se and credible intervals:

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=3.5, fig.height=2, fig.align='center'}
setwd("~/R_Projects/Reproductive traits") 
load("Data/RData/brms_m1_visits_self_all.RData")
load("Data/RData/brms_data_m1_visits_self_all.RData")
c_e <- conditional_effects(m1)
p1 <- plot(c_e, points=T,plot = FALSE)[[1]]

#Estimates, se and ci
d <- p1[[1]][,c(1,7:10)]
kable(d, "latex") %>%  kable_styling(position = "center")


```

Plot output: 

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=5, fig.height=2, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/RData/brms_m1_visits_self_all.RData")
load("Data/RData/brms_data_m1_visits_self_all.RData")

c_e <- conditional_effects(m1)
p1 <- plot(c_e, points=T,plot = FALSE)[[1]]

#ylim500
ggplot(data=p1[[1]], aes(x = autonomous_selfing_level, y = visits,color = ordered(autonomous_selfing_level))) +
  geom_point(data = all_df_2,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() +
  geom_errorbar(data=p1[[1]],mapping=aes(x=autonomous_selfing_level, ymin=lower__, ymax=upper__), width=.1, color="black")+
  geom_point(data=p1[[1]], mapping=aes(x=autonomous_selfing_level, y=estimate__), color="black") + ylab("Visits") + xlab("Selfing level")+
  theme(legend.position = "none")

```

\newpage

Set ylim max to 500 in order to improve visualization Some data points not shown.

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=5, fig.height=2, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/RData/brms_m1_visits_self_all.RData")
load("Data/RData/brms_data_m1_visits_self_all.RData")

c_e <- conditional_effects(m1)
p1 <- plot(c_e, points=T,plot = FALSE)[[1]]

#ylim500
ggplot(data=p1[[1]], aes(x = autonomous_selfing_level, y = visits,color = ordered(autonomous_selfing_level))) +
  geom_point(data = all_df_2,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() +
  geom_errorbar(data=p1[[1]],mapping=aes(x=autonomous_selfing_level, ymin=lower__, ymax=upper__), width=.1, color="black")+
  geom_point(data=p1[[1]], mapping=aes(x=autonomous_selfing_level, y=estimate__), color="black") + ylab("Visits") + xlab("Selfing level")+
  theme(legend.position = "none") + ylim(0,500)

```

Try now to logit estimates, credible intervals and points, maybe improves visualization?

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=5, fig.height=2, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/RData/brms_m1_visits_self_all.RData")
load("Data/RData/brms_data_m1_visits_self_all.RData")

c_e <- conditional_effects(m1)
p1 <- plot(c_e, points=T,plot = FALSE)[[1]]

#Prepare example with selfing level
all_df_2 <- all_df_2 %>%
  mutate(autonomous_selfing_level = fct_relevel(autonomous_selfing_level, levels=c("high", "medium", "low", "none")))
all_df_2$autonomous_selfing_level <- as.factor(all_df_2$autonomous_selfing_level)

#Log
ggplot(data=p1[[1]], aes(x = autonomous_selfing_level, y = log(visits),color = ordered(autonomous_selfing_level))) +
  geom_point(data = all_df_2,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() +
  geom_errorbar(data=p1[[1]],mapping=aes(x=autonomous_selfing_level, ymin=log(lower__), ymax=log(upper__)), width=.1, color="black")+
  geom_point(data=p1[[1]], mapping=aes(x=autonomous_selfing_level, y=log(estimate__)), color="black") + ylab("Visits") + xlab("Selfing level")+
  theme(legend.position = "none")


```

So far we haven't found big differences between groups. Also note that we have a greater number of low and none self species. This could be discussed. Keep in mind.

Now I´m going to exclude the dioecious and monoecioues species that were considered as non-selfers.

# Model 2 

```brm(visits ~ autonomous_selfing_level + (1|net_id) + (1|gr(phylo, cov = A))```

Check now the fit of the model:

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=3.5, fig.height=2, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/RData/brms_m1.1_visits_self_all.RData")
load("Data/RData/brms_data_m1.1_visits_self_all.RData")

#Model fit
pp_check(m1) + xlim(-100,2000)+ylim(0,0.02)
```

The fit seems right, check now estimates, se and credible intervals:

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=3.5, fig.height=2, fig.align='center'}
setwd("~/R_Projects/Reproductive traits") 
load("Data/RData/brms_m1_visits_self_all.RData")
load("Data/RData/brms_data_m1_visits_self_all.RData")
c_e <- conditional_effects(m1.1)
p1 <- plot(c_e, points=T,plot = FALSE)[[1]]

#Estimates, se and ci
d <- p1[[1]][,c(1,7:10)]
kable(d, "latex") %>%  kable_styling(position = "center")

```

Plot output: 

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=5, fig.height=2, fig.align='center'}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)

setwd("~/R_Projects/Reproductive traits") 
load("Data/RData/brms_m1.1_visits_self_all.RData")
load("Data/RData/brms_data_m1.1_visits_self_all.RData")

c_e <- conditional_effects(m1.1)
p1 <- plot(c_e, points=T,plot = FALSE)[[1]]

#ylim500
ggplot(data=p1[[1]], aes(x = autonomous_selfing_level, y = visits,color = ordered(autonomous_selfing_level))) +
  geom_point(data = all_df_2,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() +
  geom_errorbar(data=p1[[1]],mapping=aes(x=autonomous_selfing_level, ymin=lower__, ymax=upper__), width=.1, color="black")+
  geom_point(data=p1[[1]], mapping=aes(x=autonomous_selfing_level, y=estimate__), color="black") + ylab("Visits") + xlab("Selfing level")+
  theme(legend.position = "none")

```
